---
title: "Soon Hua's Presentation"
author: "Neo Soon Hua"
date: "8 March 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
#Knitr option to make this Rmd file not echo the R codes. Deleting the line above would result in the default, which is echo=TRUE, which would show the below-mentioned R codes, e.g. "plot(pressure)", in the slides.
```
## Title of a new slide
Contents of this new slide. Absence of blank line before the "###" below makes it NOT being recognised as a top-level sub-heading.

### Top-level sub-heading

#### Second-level sub-heading
- Bullet 1
    + Sub point
1. Point 1
2. Point 2

>- Bullet 2 on click
>- Bullet 3 on click

## Text formatting
*italicised text*

**bold text**

`twoRandomNormalValues = rnorm(2)`

***
Another new slide without a title. Absence of blank line before the "##" below makes it NOT start a new slide.
## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE, comment=""}
# comment="" to get rid of the "##" before each line of R output
summary(cars)
```

## Slide with Plot

```{r pressure, eval=FALSE}
# eval=FALSE would make it NOT run the R code
plot(pressure)
```

